Constant Error Tolerance Computational Fuzzy Extractors

### 2014-01-30 constantRate/ConstCompFuzzExt.tex
correctness of sampling construction

Together these arguments allow us to conclude:
\begin{theorem}
\label{thm:security of cons}
Let $\mathcal{O}$ be an $\ell$-composable virtual black box obfuscator with auxiliary inputs for point programs over $\zo^n$ that is $(s_{obf}, \epsilon_{obf})$-hard.  Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.  Then $H^{\hill}_{\epsilon', s_{obf}}( C | P ) \geq |C| - \beta$ for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
\end{theorem}

\noindent
We now prove $S$ cannot distinguish between $C$ and $C'$.  
Let $\mathcal{I}$ be the set of all indices in \defref{def:block guessable}.  Recall that $C'$ is a uniformly distributed codeword conditioned on agreeing with $C$ in all coordinates of $C_{\mathcal{I}^c}$.
\begin{lemma}
\label{lem:sim cannot distinguish}
$\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) \le (\ell-\beta) 2^{-(\alpha+1)}$.
\end{lemma}

@@

\textbf{Limitations of \consref{cons:first construction}:}  There are three major drawbacks to our construction.   The first is that we leak equality information about particular blocks, this may be sensitive information in the presence of auxiliary information.  Second, we obtain only a single bit from each block of $W_i$ which seems sub optimum.  Lastly, Hamming distance is computed over an alphabet of exponential size, which precludes use in some applications. We begin to address this weakness in the next section.

@@

\defref{def:unordered source} is a generalization of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), an unordered block source is one where most blocks contribute some entropy conditioned on the value of the other blocks.  This is a strengthening of an unguessable block distribution~(\defref{def:block guessable}), however we will achieve security for significantly lower entropy levels than were necessary for block unguessable distributions.  
\begin{construction}
\label{cons:sampling}
Let $n$ be a security parameter.
Let $Z$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $Z$.  Let $t$ be the desired error tolerance and let $C\subset \zo^\ell$ be a $(\neigh_t, \epsilon_{code})$ code.  Let $\sample_\beta(\gamma)$ output a uniform subset of indices of $1,..., \gamma$ of size $\beta$. Let $\eta = \omega(\log n)$ be some function such that $\eta \log (Z) = \omega(\log n)$.  Let $\mathcal{O}$ be a $\ell$-composable f for the family of point functions over $\zo^\eta$.  Define $\gen, \rep$ as:

@@

\begin{lemma}
\label{lem:sampling works}
Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma /2-\Omega(1))$-unordered block source.  Let $\eta = \Omega(\log n)$. Consider some fixed $i$, the distribution $V_{i}, J_{i, 1},..., J_{i, \eta}$ is $(\ngl(n)+ 2^{-\Omega(n)})$-close to a distribution $V', U_{\beta\times \log \gamma}$ where for all $u\in U_{\beta \times \log \gamma}$ $V' | A=a$, $\Hoo(V' | A=a) \geq \Omega(\alpha\times (1-2\times \beta) \times \eta) = \omega(\log n) = \alpha'$.\bnote{need to come up with the right number of coins for $\sample$}
\end{lemma}
\begin{proof}
By~\cite[Lemma 9]{vadhan2003constructing}, noting that the truly random sampler is optimum in necessary samples and we take $\eta = \Omega(\log n)$ samples.  \bnote{need someone to check parameters, I am fairly sure of the quality of the statement}
\end{proof}
%\begin{align*}
%\expe[\Hoo(V_i)] &=\expe[\text{entropy of each uniform }w_j] (\text{number of }w_j\text{ selected})\\
%&=\frac{\lambda}{\gamma} \times \eta= \frac{\lambda \eta}{\gamma}.
%\end{align*}
%This value is super-logarithmic when $\lambda = \omega (\frac{\gamma \log n}{\eta})$.  Note this is independent of how the entropy is distributed between blocks.  In particular, we make no assumptions about particular blocks being unguessable, only about the overall entropy rate.  This is a much more natural condition for a source than \defref{def:block guessable}.  
%To show security we need the entropy of all $v_i$ to be $\omega(\log n)$ with overwhelming probability.  This follows by an argument from the locally computable extractor literature.

@@

\begin{corollary}
\label{cor:samp unguess}
Let $n, Z, W, \epsilon_{sam}$ be as in \corref{cor:samp sec} and let $\mathcal{O}$ is an $\ell$-composable virtual black obfuscator with auxiliary inputs for point programs over $\zo^{\beta\times \log |Z|}$ that is $(s_{obf}, \epsilon_{obf})$-hard, then $H^{\hill}_{\epsilon', s_{obf}}(C | P) \geq |C|$ for $\epsilon' = (2\epsilon_{obf} + \epsilon_{sam}+ 2^{-(\alpha-1)}) = \ngl(n)$.
\end{corollary}
\begin{proof}
Result of \corref{cor:v are unguessable} and \thref{thm:security of cons}.
\end{proof}

\subsection{Correctness of \consref{cons:sampling}}
The argument that $1\rightarrow 0$ flips are unlikely carries over from \consref{cons:first construction}.  Let $t'$ be the capacity of $C$.  To show correctness we must show that with overwhelming probability $\dis(v, v')\leq t'$.  Let $t$ be the number of supported errors between $w$ and $w'$.  Let $c>0$ and let $t = c(\gamma-\eta)/\eta$, for any  $i$ one has:
% In this section, we analyze what values of $t$ will yield a small constant likelihood of error between $v_i$ and $v_i'$ yielding a constant probability of bit flip $0\rightarrow 1$ between $c$ and $c'$.  Consider a single index $i$ and let $t$ be the number of errors between $w$ and $w'$.  Then 
\begin{align*}
\expe \Pr[v_i = v_i'] &=\Pr[j_{i,1},..., j_{i,\eta}\text{ have no errors}]\\
&\geq \prod_{j=0}^{\eta-1}\left(1 - \frac{t}{\gamma-j}\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{c(\gamma-\eta)/\eta}{\gamma-i}\right)\\
&\geq  \prod_{j=0}^{\eta-1}\left( 1-\frac{c}{\eta}\left(\frac{\gamma-\eta}{\gamma-j}\right)\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{c}{\eta}\right) \\
&\geq \left(1-\frac{c}{\eta}\right)^{\eta} =\left( \left(1-\frac{c}{\eta}\right)^{\eta/c}\right)^c\geq \frac{1}{4}^c
\end{align*} 
Thus, by setting $c = -\log(1-t')/2$ we obtain in $\expe[\dis(v, v')\leq t']$.  We need a stronger condition that this occurs with overwhelming probability.

\bnote{finish, Chernoff, not far from expectation.}

\subsection{Discussion}
\bnote{need to write this once we have parameters in the two sections above.}
%As shown above we get security when $\lambda = \omega(\gamma \log n/\eta)$ and correctness when $t = \Theta(\gamma /\eta)$.  This yields:
%\begin{align*}
%gap &= \Hoo(W) -\log |B_t| \\
%&< \omega(\frac{\gamma  \log n}{\eta} ) - (\Theta(t \mu) + \log {\gamma \choose t})\\
%&= \omega(\frac{\gamma \log n}{\eta}) - (\Theta(\frac{\gamma \mu^2}{\eta}))\\
%&= \omega(\frac{\gamma \log n}{\eta}) - (\Theta(\frac{\gamma \log |Z|}{\eta}))\\
%&= \omega(\frac{\gamma \log n}{\eta})
%\end{align*}
%%Taking $\gamma = \Omega(n)$ and $\eta = \log^c n$ yields a negative $gap$.
%\bnote{finish}
\bibliographystyle{alpha}
\bibliography{crypto}

@@

>>>>

\noindent Together these arguments allow us to conclude:
\begin{theorem}
\label{thm:security of cons}
Let $\mathcal{O}$ be an $\ell$-composable virtual black box obfuscator with auxiliary inputs for point programs over $\zo^n$ that is $(s_{obf}, \epsilon_{obf})$-hard.  Let $W$ be a $(s_{obf}, \alpha = \omega(\log n), \beta)$-unguessable block distribution.  Then $H^{\hill}_{\epsilon', s_{obf}}( C | P ) \geq |C| - \beta$ for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
\end{theorem}

@@

\textbf{Limitations of \consref{cons:first construction}:}  There are three major drawbacks to our construction.   The first is that we leak equality information about particular blocks, this may be sensitive information in the presence of auxiliary information.  Second, we obtain only a single bit from each block of $W_i$ which seems sub optimum.  Lastly, Hamming distance is computed over an alphabet of exponential size, which precludes use in some applications. We begin to address this weakness in the next section.\bnote{come back to this linking language}

@@

\defref{def:unordered source} is a generalization of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), an unordered block source is one where most blocks contribute some entropy conditioned on the value of the other blocks.  This is a strengthening of an unguessable block distribution~(\defref{def:block guessable}), however we will achieve security for significantly lower entropy levels than were necessary for block unguessable distributions.  
\begin{construction}
\label{cons:sampling}
Let $n$ be a security parameter.
Let $Z$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $Z$ and $\gamma = Omega(n )$.  Let $t$ be the desired error tolerance and let $C\subset \zo^\ell$ be a $(\neigh_t, \epsilon_{code})$ code.  Let $\sample_\beta(\gamma)$ output a uniform subset of indices of $1,..., \gamma$ of size $\beta$. Let $\eta = \omega(\log n)$ be some function such that $\eta \log (Z) = \omega(\log n)$.  Let $\mathcal{O}$ be a $\ell$-composable f for the family of point functions over $\zo^\eta$.  Define $\gen, \rep$ as:

@@

\begin{lemma}
\label{lem:sampling works}
Let $W = W_1,..., W_\gamma$ be a $(\alpha = \Omega(1), \beta \leq \gamma(1/2-\Theta(1))$-unordered block source.  Let $\eta = \Omega(\log n)$. Consider some fixed $i$, the distribution $V_{i}, J_{i, 1},..., J_{i, \eta}$ is $(\ngl(n)+ 2^{-\Omega(n)})$-close to a distribution $V', U_{\beta\times \log \gamma}$ where for all $u\in U_{\beta \times \log \gamma}$ $V' | A=a$, $\Hoo(V' | A=a) \geq \Omega(\alpha\times (1-2\times \beta) \times \eta) = \omega(\log n) = \alpha'$.\bnote{need to come up with the right number of coins for $\sample$}
\end{lemma}
\begin{proof}
By~\cite[Lemma 9]{vadhan2003constructing}, noting that the truly random sampler is optimum in necessary samples and we take $\eta = \Omega(\log n)$ samples.  \bnote{need someone to check parameters, I am fairly sure of the quality of the statement}
\end{proof}
%\begin{align*}
%\expe[\Hoo(V_i)] &=\expe[\text{entropy of each uniform }w_j] (\text{number of }w_j\text{ selected})\\
%&=\frac{\lambda}{\gamma} \times \eta= \frac{\lambda \eta}{\gamma}.
%\end{align*}
%This value is super-logarithmic when $\lambda = \omega (\frac{\gamma \log n}{\eta})$.  Note this is independent of how the entropy is distributed between blocks.  In particular, we make no assumptions about particular blocks being unguessable, only about the overall entropy rate.  This is a much more natural condition for a source than \defref{def:block guessable}.  
%To show security we need the entropy of all $v_i$ to be $\omega(\log n)$ with overwhelming probability.  This follows by an argument from the locally computable extractor literature.

@@

\begin{corollary}
\label{cor:samp unguess}
Let $n, Z, W, \epsilon_{sam}$ be as in \corref{cor:samp sec} and let $\mathcal{O}$ is an $\ell$-composable virtual black obfuscator with auxiliary inputs for point programs over $\zo^{\beta\times \log |Z|}$ that is $(s_{obf}, \epsilon_{obf})$-hard, then $H^{\hill}_{\epsilon', s_{obf}}(C | P) \geq |C|$ for $\epsilon' = (2\epsilon_{obf} + \epsilon_{sam}+ 2^{-(\alpha''-1)}) = \ngl(n)$.
\end{corollary}
\begin{proof}
Result of \corref{cor:v are unguessable} and \thref{thm:security of cons}.
\end{proof}

\subsection{Correctness of \consref{cons:sampling}}
The argument that $1\rightarrow 0$ flips are unlikely carries over from \consref{cons:first construction}.  Let $t'$ be the capacity of $C$.  To show correctness we must show that with overwhelming probability $\dis(v, v')\leq t'$.  Let $t$ be the number of supported errors between $w$ and $w'$.  Let $c>0$ and let $t = c(\gamma-\eta)/\eta$, for any  $i$ one has:
% In this section, we analyze what values of $t$ will yield a small constant likelihood of error between $v_i$ and $v_i'$ yielding a constant probability of bit flip $0\rightarrow 1$ between $c$ and $c'$.  Consider a single index $i$ and let $t$ be the number of errors between $w$ and $w'$.  Then 
\begin{align*}
\expe \Pr[v_i = v_i'] &=\Pr[j_{i,1},..., j_{i,\eta}\text{ have no errors}]\\
&\geq \prod_{j=0}^{\eta-1}\left(1 - \frac{t}{\gamma-j}\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{c(\gamma-\eta)/\eta}{\gamma-i}\right)\\
&\geq  \prod_{j=0}^{\eta-1}\left( 1-\frac{c}{\eta}\left(\frac{\gamma-\eta}{\gamma-j}\right)\right)\geq \prod_{j=0}^{\eta-1}\left( 1-\frac{c}{\eta}\right) \\
&\geq \left(1-\frac{c}{\eta}\right)^{\eta} =\left( \left(1-\frac{c}{\eta}\right)^{\eta/c}\right)^c\geq \frac{1}{4}^c
\end{align*} 
Thus, by setting $c = -\log(1-t'/\ell)/2$ we obtain in $\expe[\dis(v, v')\leq t']$.  We need a stronger condition that this occurs with overwhelming probability.

\begin{lemma}
Let $n, W$ be as above and Let $C$ be a code that corrects $t$ $0\rightarrow 1$ bit errors where $t =\Theta(\eta)$.  Let $c = -\log(1-t'/(2\ell))/2 = \Theta(1)$, when $t \leq c(\gamma - \eta)/\eta$, then $\Pr[\dis(v, v')\leq t']\geq 1-O(2^{-\ell})$ where the probability is over the coins of $\gen$.
\end{lemma}
\begin{proof}
With each $i$ we can associate a Bernoulli random variable $X_i \overset{def}= V_i \overset{?}\neq V_i'$.  As stated above, we have that $\expe[X_i] \leq 1-\frac{1}{4}^c = t'/(2\eta)$. By the Chernoff bound, we have
\begin{align*}
\Pr\left[\frac{1}{\eta} \sum_{i=1}^\eta X_i\geq 2\expe[X_i]\right]\leq 2e^{-2\expe[X_i]\eta} = O(e^{- \ell}) 
\end{align*}
\end{proof}

\begin{corollary}
Let $\ell = \omega(\log n)$ and let $C\subset\zo^\ell$ and  be a code that corrects $t' = \Theta(\ell)$ $0\rightarrow 1$ bit errors.  Then when 
\[
\dis(w, w')\leq \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta} = O(\frac{\gamma-\eta}{\eta}) = O(\gamma/\eta)
\] 
and $(R, P)\leftarrow \gen(w)$, then 
\[
\Pr[\rep( w', P) = R] \geq 1-\frac{\ell}{2^n} - O(2^{-\ell}) = 1-\ngl(n).
\]
That is, \consref{cons:sampling} is correct with error at most $\ngl(n)$.

\end{corollary}
\subsection{Discussion of \consref{cons:sampling}}
We now show that \consref{cons:sampling} achieves $gap<0$ for an interesting setting of parameters.  For security of an unordered block source we needed both $\alpha = \Theta(1)$ and $\beta\leq \gamma/2-\Omega(1)$.  This means that the overall required entropy of $\Hoo(W) = \Theta(\gamma)$.  We are able to correct $O(\gamma/\eta)$ errors
This yields:
\begin{align*}
gap &= \Hoo(W) -\log |B_t| \\
&< \Theta(\gamma)- t \log |Z|\\
&= \Theta(\gamma) - O(\gamma/\eta) \log |Z|\\
\end{align*}
That is, \consref{cons:sampling} achieves $gap<0$ when the starting alphabet is super polynomial~(noting that for any fixed $Z$ we can set $\eta = \omega(\log n)$ and $\eta = o(\log |Z|)$).  If we are willing to accept $gap\geq 0$ then \consref{cons:sampling} works for polynomial size alphabet $Z$.
\bibliographystyle{alpha}
\bibliography{crypto}

@@

\section{Proof of \thref{thm:security of cons}}
\noindent
We now prove $S$ cannot distinguish between $C$ and $C'$.  
Let $\mathcal{I}$ be the set of all indices in \defref{def:block guessable}.  Recall that $C'$ is a uniformly distributed codeword conditioned on agreeing with $C$ in all coordinates of $C_{\mathcal{I}^c}$.
\begin{lemma}
\label{lem:sim cannot distinguish}
$\Delta(S^{\mathcal{O}_X(\cdot, \cdot)}(C), S^{\mathcal{O}_X(\cdot, \cdot)}(C')) \le (\ell-\beta) 2^{-(\alpha+1)}$.
\end{lemma}
